Multi-Resolution Neural Field Estimation

### 2011-03-13 Multiresolution_framework/ltx/manuscript.tex
edits to keywords
minor correction

\begin{abstract}
%\boldmath
We develop a multi-resolution approximation (MRA) framework for the integro-difference equation (IDE) neural field model based on semi-orthogonal cardinal B-spline wavelets. State and parameter estimation is performed using the Expectation Maximization (EM) algorithm. A synthetic example is provided
to demonstrate the framework.
\end{abstract}
% Note that keywords are not normally used for peerreview papers.
 \begin{IEEEkeywords}
  Neural field model, multiresolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
  \end{IEEEkeywords}
% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
%   \begin{center} \bfseries EDICS Category: SSP-IDEN \end{center}
%   \fi
%
%  For peerreview papers, this IEEEtran command inserts a page break and
%creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

@@

To derive the state-space model, we first define the matrices 
\begin{align}\label{eq:Lambdax}
 \mathbf{\Lambda}_{x} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right)\boldsymbol\mu^\top\left(r\right) dr \\
\label{eq:Lambdatheta}
 \mathbf{\Lambda}_{\theta} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right) \int_\Omega { 
	   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
	    \boldsymbol\mu^\top\left(r\right)\ dr'dr.}
\end{align}
Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multiplying by $\boldsymbol\mu\left(\mathbf r\right)$, and integrating over the space gives
\begin{align}\label{eq:DecomposedModel2} 
	&\mathbf{\Lambda}_{x} \mathbf{x}_{t+1}= 
	\xi\mathbf{\Lambda}_{x} \mathbf{x}_t +T_s \varsigma \mathbf{\Lambda}_{\theta}\mathbf{x}_t +\int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)dr.
\end{align}
Cross-multiplying by $\mathbf{\Lambda}_{x}^{-1}$ gives the state transition equation
\begin{align}\label{eq:StateEquation}
 \mathbf x_{t+1} &=\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t\\
\label{eq:A_theta}
 \mathbf A(\boldsymbol \theta) &= T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I,
\end{align}
where $\mathbf I$ is the identity matrix. The disturbance becomes 
\begin{equation}\label{eq:Disturbance}
\mathbf w_t= \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol\mu \left(r\right)e_t\left(r\right)dr,
\end{equation}
which is a vector valued, zero-mean normally distributed, white noise process with covariance (see \cite{Freestone2011} for proof)
\begin{equation}
\boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\boldsymbol\Omega}\boldsymbol\mu\left(r\right) \eta\left(r-r'\right)\boldsymbol\mu^{\top}\left(r'\right)dr'dr\mathbf{\Lambda}_{x}^{-\top}.
\end{equation}
The observation equation of the state-space model is found by substituting decomposition \eqref{eq:FieldFiniteExpansion}
 into \eqref{eq:ObservationEquation} giving
\begin{equation}\label{eq:ReducedObservationEquation} 
	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
\end{equation}
where each element of the observation matrix is given by
\begin{equation}\label{eq:Observationmatrix}
	\mathbf{C}_{ij} \triangleq \int_{\Omega}m(r_i - r')\boldsymbol{\mu}_j(r') \, d\mathbf{r}'.
\end{equation}

>>>>

\begin{abstract}
%\boldmath
We develop a multi-resolution approximation (MRA) framework for the integro-difference equation (IDE) neural field model based on semi-orthogonal cardinal B-spline wavelets. State and parameter estimation is performed using the Expectation Maximization (EM) algorithm. A synthetic example is provided
to demonstrate the framework.
\end{abstract}
% Note that keywords are not normally used for peerreview papers.
 \begin{IEEEkeywords}
  Neural field model, multi-resolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
  \end{IEEEkeywords}
% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
%   \begin{center} \bfseries EDICS Category: SSP-IDEN \end{center}
%   \fi
%
%  For peerreview papers, this IEEEtran command inserts a page break and
%creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

@@

To derive the state-space model, we first define the matrices 
\begin{align}\label{eq:Lambdax}
 \mathbf{\Lambda}_{x} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right)\boldsymbol\mu^\top\left(r\right) dr \\
\label{eq:Lambdatheta}
 \mathbf{\Lambda}_{\theta} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right) \int_\Omega { 
	   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
	    \boldsymbol\mu^\top\left(r\right)\ dr'dr.}
\end{align}
Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multiplying by $\boldsymbol\mu\left(r\right)$, and integrating over the space gives
\begin{align}\label{eq:DecomposedModel2} 
	&\mathbf{\Lambda}_{x} \mathbf{x}_{t+1}= 
	\xi\mathbf{\Lambda}_{x} \mathbf{x}_t +T_s \varsigma \mathbf{\Lambda}_{\theta}\mathbf{x}_t +\int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)dr.
\end{align}
Cross-multiplying by $\mathbf{\Lambda}_{x}^{-1}$ gives the state transition equation
\begin{align}\label{eq:StateEquation}
 \mathbf x_{t+1} &=\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t\\
\label{eq:A_theta}
 \mathbf A(\boldsymbol \theta) &= T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I,
\end{align}
where $\mathbf I$ is the identity matrix. The disturbance becomes 
\begin{equation}\label{eq:Disturbance}
\mathbf w_t= \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol\mu \left(r\right)e_t\left(r\right)dr,
\end{equation}
which is a vector valued, zero-mean normally distributed, white noise process with covariance (see \cite{Freestone2011} for proof)
\begin{equation}
\boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\boldsymbol\Omega}\boldsymbol\mu\left(r\right) \eta\left(r-r'\right)\boldsymbol\mu^{\top}\left(r'\right)dr'dr\mathbf{\Lambda}_{x}^{-\top}.
\end{equation}
The observation equation of the state-space model is found by substituting decomposition \eqref{eq:FieldFiniteExpansion}
 into \eqref{eq:ObservationEquation} giving
\begin{equation}\label{eq:ReducedObservationEquation} 
	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
\end{equation}
where each element of the observation matrix is given by
\begin{equation}\label{eq:Observationmatrix}
	\mathbf{C}_{ij} \triangleq \int_{\Omega}m(r_i - r')\boldsymbol{\mu}_j(r') \, d\mathbf{r}'.
\end{equation}
